Offshore Blue Crab Densities for <br/> The Gulf of Mexico

### 2020-01-23 2019_edits/R/offshore_analyses/crabs_per_hectare.Rmd
updated manuscript figures and models

```{r}
rs_plot_1 <- rs_summary %>% 
  ggplot(aes(region, `Mean Catch`, fill = Season)) +
    geom_col(position = "dodge") +
    geom_errorbar(aes(ymin = catch_ymin,
                      ymax = catch_ymax),
                  position = "dodge", 
                  size = .25) +
  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
  labs(x = "Survey Year",
       y = "Mean Catch (C. sapidus / Hectare)") + theme(
    legend.position = c(1, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA),
    axis.text.x = element_text(angle = 45, vjust = 0.5)
    )

@@

rs_plot_2 <- rs_summary %>% 
  ggplot(aes(region, `% Occurrence`, fill = Season)) +
    geom_col(position = "dodge") +
    geom_errorbar(aes(ymin = occurrence_ymin,
                      ymax = occurrence_ymax),
                  position = "dodge",
                  size = .25) +
  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
  labs(x = "Survey Year",
       y = "Percent Occurrence") + theme(
    legend.position = c(1, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA),
    axis.text.x = element_text(angle = 45, vjust = 0.5)
    )

@@

@@

>>>>

```{r}
rs_plot_1 <- rs_summary %>% 
  ggplot(aes(region, `Mean Catch`, fill = Season)) +
    geom_col(position = "dodge") +
    geom_errorbar(aes(ymin = catch_ymin,
                      ymax = catch_ymax),
                  position = "dodge", 
                  size = .25) +
  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
  labs(x = "Region",
       y = "Mean Catch (C. sapidus / Hectare)") + theme(
    legend.position = c(1, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA),
    axis.text.x = element_text(angle = 45, vjust = 0.5)
    )

@@

rs_plot_2 <- rs_summary %>% 
  ggplot(aes(region, `% Occurrence`, fill = Season)) +
    geom_col(position = "dodge") +
    geom_errorbar(aes(ymin = occurrence_ymin,
                      ymax = occurrence_ymax),
                  position = "dodge",
                  size = .25) +
  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
  labs(x = "Region",
       y = "Percent Occurrence") + theme(
    legend.position = c(1, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA),
    axis.text.x = element_text(angle = 45, vjust = 0.5)
    )

@@

*NOTE: Zeros removed for plotting*

```{r}
seamap_west %>% 
  mutate(year = as.numeric(as.character(year_f))) %>% 
  filter(cpue_towspd > 0) %>% 
  ggplot(aes(year, cpue_towspd)) +
  #geom_boxplot(aes(group = year)) +
  geom_boxplot(aes(group = year), outlier.shape = NA) +
  ylim(0, 2) +
  labs(x = NULL, y = "Crabs / Hectare")
```

@@

*NOTE: Zeros removed for plotting*

```{r}
region_plot_west <- seamap_west %>% 
  filter(cpue_towspd > 0) %>% 
  ggplot(aes(region, cpue_towspd)) +
  geom_boxplot(aes(fill = season), outlier.shape = NA) +
   scale_fill_grey(start = 0.3, end = 0.5) +
  ylim(0, 2) +
  labs(x = NULL, y = "Crabs / Hectare") + 
  theme(
    legend.title = element_blank(),
    legend.position = c(1, .98),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA)
    )

season_plot_west <- seamap_west %>% 
    group_by(region, season) %>% 
    summarise(
      stations = n(),
      `missing obs`     = sum(is.na(cpue_towspd)),
      `% Occurrence` = mean(crab_presence, na.rm = T),
      `% Occurrence SE` = sd(crab_presence, na.rm = T) / sqrt(stations - `missing obs`)) %>% 
    mutate(
      occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
      occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
      occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
    ) %>% 
  ggplot(aes(region, `% Occurrence`)) +
    geom_pointrange(aes(ymin = occurrence_ymin, 
                        ymax = occurrence_ymax, 
                        shape = season, 
                        color = season)) +
    scale_color_grey(start = 0.3, end = 0.5) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    labs(x = NULL, y = "Percent Occurrence") + 
  theme(
    legend.title = element_blank(),
    legend.position = c(1, .98),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA)
    )

region_plot_west + season_plot_west
